My title

### 2024-03-12 paper/paper.qmd
Edits

---
title: "My title"
author: "Bernice(Yixuan) Bao, Zheng(Zeb) Yang, Dongli Sun"
thanks: "Code and data are available at: LINK."
date: "March 11, 2024"
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

@@

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = "none") +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

@@

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

analysis_data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))

analysis_data |> 
  ggplot(aes(x = width, y = length)) +
  geom_point(alpha = 0.8) +
  theme_minimal() +
  labs(x = "Wing width (mm)",
       y = "Wing length (mm)")
```

@@

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

@@

Our results are summarized in @tbl-modelresults.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

library(rstanarm)

first_model <-
  readRDS(file = here::here("models/first_model.rds"))
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

modelsummary::modelsummary(
  list(
    "First model" = first_model
  ),
  statistic = "mad",
  fmt = 2
)
```

```{r}
#| echo: false
#| eval: true
#| label: fig-modelresultsfig
#| fig-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

modelplot(first_model, conf_level = 0.9) +
  labs(x = "90 per cent credibility interval")
```

@@

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

@@

## Posterior predictive check

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

analysis_data <- arrow::read_parquet(here::here("data/analysis_data/analysis_data.parquet"))

set.seed(853)

analysis_data <- 
  analysis_data |> 
  slice_sample(n = 1000)

pp_check(first_model) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(first_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

## Diagnostics

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2

plot(first_model, "trace")

plot(first_model, "rhat")
```

>>>>

---
title: "My title"
author: "Bernice(Yixuan) Bao, Zheng(Zeb) Yang, Dongli Sun"
thanks: "Code and data are available at: <https://github.com/iloveyz12/US-Political-Support>."
date: "March 11, 2024"
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

We use the dataset from 2022 Cooperative Election Study @ces2022. To further enable the analysis I employed the use of the package of ggplot[@ggplot2] to generate histograms.

@@

```{r}
#| echo: false
#| warning: false
#| message: false
ces2022 <-
  read_csv(
    here::here("data/raw_data/ces2022.csv"),
    col_types =
      cols(
        "votereg" = col_integer(),
        "presvote20post" = col_integer(),
        "gender4" = col_integer(),
        "educ" = col_integer()
      )
  )

ces2022 <-
  ces2022 |>
  filter(votereg == 1,
         presvote20post %in% c(1, 2)) |>
  mutate(
    voted_for = if_else(presvote20post == 1, "Biden", "Trump"),
    voted_for = as_factor(voted_for),
    gender = case_when(
      gender4 == 1 ~ "Man", 
      gender4 == 2 ~ "Woman", 
      gender4 == 3 ~ "Non-binary", 
      gender4 == 4 ~ "Other"),
    education = case_when(
      educ == 1 ~ "No HS",
      educ == 2 ~ "High school graduate",
      educ == 3 ~ "Some college",
      educ == 4 ~ "2-year",
      educ == 5 ~ "4-year",
      educ == 6 ~ "Post-grad"
    ),
    education = factor(
      education,
      levels = c(
        "No HS",
        "High school graduate",
        "Some college",
        "2-year",
        "4-year",
        "Post-grad"
      )
    )
  ) |>
  select(voted_for, gender, education)
```

@@

@@

```{r}
#| echo: false
#| warning: false
#| message: false
#| include: false

set.seed(812)

ces2022_reduced <- 
  ces2022 |> 
  slice_sample(n = 1000)

political_preferences <-
  stan_glm(
    voted_for ~ gender + education,
    data = ces2022_reduced,
    family = binomial(link = "logit"),
    prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
    prior_intercept = 
      normal(location = 0, scale = 2.5, autoscale = TRUE),
    seed = 853
  )

saveRDS(
  political_preferences,
  file = "political_preferences.rds"
)
```

```{r}
#| echo: false
#| warning: false
#| message: false
political_preferences <-
  readRDS(file = "political_preferences.rds")
```

```{r}
#| label: tbl-vote
#| tbl-cap: "Whether a respondent is likely to vote for Biden based on their gender and education"
#| echo: false
#| warning: false
#| message: false
modelsummary(
  list(
    "Support Biden" = political_preferences
  ),
  statistic = "mad"
  )
```

@@

Our results are summarized in @fig-vote.

```{r}
#| label: fig-vote
#| fig-cap: ""
#| echo: false
#| eval: true
#| warning: false
#| message: false

ces2022 |>
  ggplot(aes(x = education, fill = voted_for)) +
  stat_count(position = "dodge") +
  facet_wrap(facets = vars(gender)) +
  theme_minimal() +
  labs(
    x = "Highest education",
    y = "Number of respondents",
    fill = "Voted for"
  ) +
  coord_flip() +
  scale_fill_brewer(palette = "Set1") +
  theme(legend.position = "bottom")
```

@@

@@
